### 2024-07-20 mythbusters.qmd
20240720 - effect size

```{r}
library("petersenlab")
library("lme4")
library("lmerTest")
library("tidyverse")
```

@@

summary(mixedModel_qbr)
```

@@

summary(mixedModel_ptsAdded)
```

@@

summary(mixedModel_epaPass)
```

@@

summary(mixedModel_ypc)
```

@@

summary(mixedModel_epaRush)
```

@@

summary(mixedModel_receivingYards)
```

@@

summary(mixedModel_epaReceiving)
```

>>>>

```{r}
library("petersenlab")
library("lme4")
library("lmerTest")
library("MuMIn")
library("tidyverse")
```

@@

summary(mixedModel_qbr)
MuMIn::r.squaredGLMM(mixedModel_qbr)
```

@@

summary(mixedModel_ptsAdded)
MuMIn::r.squaredGLMM(mixedModel_ptsAdded)
```

@@

summary(mixedModel_epaPass)
MuMIn::r.squaredGLMM(mixedModel_epaPass)
```

@@

summary(mixedModel_ypc)
MuMIn::r.squaredGLMM(mixedModel_ypc)
```

@@

summary(mixedModel_epaRush)
MuMIn::r.squaredGLMM(mixedModel_epaRush)
```

@@

summary(mixedModel_receivingYards)
MuMIn::r.squaredGLMM(mixedModel_receivingYards)
```

@@

summary(mixedModel_epaReceiving)
MuMIn::r.squaredGLMM(mixedModel_epaReceiving)
```
